\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-04-28 draft.tex
add notes about not repeating explanation of uncertainty; closes #22
add justification for eqm selection criterion; closes #23

Second, whenever there is a possibility of multiple equilibria, I will focus on the one that maximizes the welfare of the executives.

@@

Alternatively, the integration of the random variable $\ta$ can represent reduced-form modeling of political uncertainty arising from a complex decision-making process within a legislature. One can interpret $\ta$ as measuring uncertainty over the identity of the median legislator in order to represent the idea that the lobbying and voting ``game'' that goes on within legislatures is often complex enough that none of the actors know precisely what the outcome will be---that is, no one can predict exactly which legislator will be the median and therefore what weight will be placed on import-industry profits at the time of the vote. Thus one way we can think about $\ta$ is as an additional influence on the legislature's preferences about which all parties---executives, legislators and lobbies alike---are uncertain. It is this interpretation of $\ta$ I take throughout this paper.

One can conceptualize this uncertainty as being a result of the lobby's strategic choice to engage with only some key members of the legislature who wield significant influence but who cannot deliver policy decisions without the cooperation of others within the legislature, which is in turn uncertain. Different assumptions on $\ga(\cdot,\cdot)$ correspond to different institutional features and will affect optimal lobbying- and tariff-setting behavior. I make the following two basic assumptions on the weight on import-industry profits:

>>>>

Second, whenever there is a possibility of multiple equilibria, I focus on the one that maximizes the welfare of the executives. Given the assumption that the executives are social welfare maximizers, this selection criterion puts results in terms of the maximal level of trade policy cooperation that is possible. It also allows the question of whether governments use trade agreements as political commitment devices to be answered in a straightforward way.

@@

Alternatively, the integration of the random variable $\ta$ can represent reduced-form modeling of political uncertainty arising from a complex decision-making process within a legislature. One can interpret $\ta$ as measuring uncertainty over the identity of the median legislator in order to represent the idea that the lobbying and voting ``game'' that goes on within legislatures is often complex enough that none of the actors know precisely what the outcome will be---that is, no one can predict exactly which legislator will be the median and therefore what weight will be placed on import-industry profits at the time of the vote. Thus one way we can think about $\ta$ is as an additional influence on the legislature's preferences about which all parties---executives, legislators and lobbies alike---are uncertain. It is this interpretation of $\ta$ I take throughout this paper. %need to keep this paragraph and the next, or at least parts of it, to satisfy #22

One can conceptualize this uncertainty as being a result of the lobby's strategic choice to engage with only some key members of the legislature who wield significant influence but who cannot deliver policy decisions without the cooperation of others within the legislature, which is in turn uncertain. Different assumptions on $\ga(\cdot,\cdot)$ correspond to different institutional features and will affect optimal lobbying- and tariff-setting behavior. I make the following two basic assumptions on the weight on import-industry profits: %need to keep this paragraph and the previous, or at least parts of them, to satisfy #22
